partial: An R Package for Creating Partial Dependence Plots

### 2016-07-12 manuscript/greenwell.tex
first draft -- rough

\abstract{
An abstract of less than 150 words.
}

@@

As described in the introduction, the \pkg{partial} package is useful for constructing PDPs for many types of fitted models in R. These are especially useful for visualizing the relationships discovered by complex machine learning algorithms such as a random forest. The latest stable release is available from CRAN:
\begin{example}
install.packages("partial")
\end{example}
%low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$

>>>>

\abstract{
Complex predictive models (e.g., neural networks, random forests, and support vector machines) offer much promise in the world of data analytics, especially when dealing with large observational databases that don't adhere to the strict assumptions imposed by traditional statistical techniques (e.g. multiple linear regression). Unfortunately though, it can be challenging for the uninitiated to understand the results of such models and explain them to management. Partial dependence plots offer a simple solution. Partial dependence plots offer low-dimensional graphical renderings of the prediction function $\widehat{f}\left(\boldsymbol{x}\right)$ so that the relationship between the outcome and predictors of interest can be easily understood. These plots are especially useful in explaining the output from complex black box models like support vector machines or neural networks or constructing simpler parsimonious models on newly obtained data. 
}

@@

As described in the introduction, the \pkg{partial} package is useful for constructing PDPs for many types of fitted models in R. These are especially useful for visualizing the relationships discovered by complex machine learning algorithms such as a random forest. The latest stable release is available from CRAN:
\begin{example}
install.packages("partial")
\end{example}
